---
title: "Blood and Wine: The Wild Hunt"
output: 
  flexdashboard::flex_dashboard:
runtime: shiny
---
```{r setup, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(readr)
wine <- read_csv("winemag-data_first150k_recoded_countries.csv")
mapPolys <- geojsonio::geojson_read("countries.geo.json", what = "sp")
```

Page 1 - Histogram and Chloropleths  {data-orientation=rows}
=====================================  

Inputs {.sidebar}
-------------------------------------
This is the side bar where we put our shit. to select what's gonna be displayed in the chlorpleth

```{r}
# shiny inputs defined here
selectInput(inputId = "variety", label = "Wine Variety", choices = wine$variety, selected = NULL, multiple = TRUE, selectize = TRUE, width = NULL, size = NULL)

selectInput(inputId = "country", label = "Country", choices = wine$country, selected = NULL, multiple = FALSE, selectize = TRUE, width = NULL, size = NULL)

sliderInput(inputId = "pointRange", label = "Points Between", min = 75, max = 100, value= c(90,100), step = NULL, round = FALSE,
  format = NULL, locale = NULL, ticks = TRUE, animate = FALSE,
  width = NULL, sep = ",", pre = NULL, post = NULL, timeFormat = NULL,
  timezone = NULL, dragRange = TRUE)


sliderInput(inputId = "priceRange", label = "Price Between", min = 0, max = 10000, value= c(10,100), step = NULL, round = FALSE,
  format = NULL, locale = NULL, ticks = TRUE, animate = FALSE,
  width = NULL, sep = ",", pre = NULL, post = NULL, timeFormat = NULL,
  timezone = NULL, dragRange = TRUE)
```


Row {data-height=350}
-------------------------------------
    
### Histogram: Price Distribution given the selected features
insert histogram on world wide distribution of prices
or maybe can put a selection toggle to switch between histogram and kernel density plot. or to overlay.
```{r}
```
    
Row {data-height=600 .tabset .tabset-fade}
-------------------------------------    

### Chloropleth  of Prices
Insert Chloropleth world map of places where prices are high. Red for high, blue for low.
I guess for interactive stuff, we need to use plotly.
```{r}
```

### Chloropleth of Frequency
insert chloropleth world map of places where frequency is highest.
```{r}
```

Page 2 - Topic Modelling on Wine Descriptions  {data-orientation=rows}
=====================================  

Row {data-height=350}
-------------------------------------
    
### Topic Modelling on Wine Descriptions
    
```{r}
```

Column {data-height=650 }
-------------------------------------    

### LDA
insert bubble plot of intertopic distance map (via multidimensional scaling)
```{r}
```

### LDA2
insert top 30 most relevant terms for topic (3.5% of tokens)
```{r}
```

Row {data-height=150}
-------------------------------------

### Summary
When you click/hover on one circle, the top 20-30 words appear in this box to summarize the flavour.
```{r}
```

Row {data-height=350}
-------------------------------------
### TF-IDF Relevance by Winery
Insert TF-IDF bar chart.
```{r}

```


