---
title: "Blood and Wine: The Wild Hunt"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---
  
  ```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
library(readr)
# load data
wine_master <- read_csv("data/mastersetof_fullscopedata_deduped.csv")
wine_bottles <- read_csv("data/beta_spread_wine_bottles.csv")
mapPolys <- geojsonio::geojson_read("data/countries.geo.json", what = "sp")
```

Identify your favourite flavours >> {data-orientation=rows}
===============================================================

Row {data-height = 150}
------------------------

Didn't you know there are many many ways to look at wine? Explore some ways below.

Row {.tabset, data-height = 500}
--------------------------------
### Pricing

```{r}

```

### Variety

```{r}
```

### Review Ratings

```{r}
```

### Country
```{r}

```
Sample the relationships >>
===========================

Row {data-height = 150}
------------------------

See how the different brands are related to each other

Row {.tabset, data-height = 500}
--------------------------------
### Prices for different countries

```{r}

```

### Ratings for different prices

```{r}
```

### Ratings for different varieties

```{r}
```





Locate your favourite flavours >>
=================================

Chloropleths go here

***
  
Here is a world map. Enter some words to search for a particular flavour profile from our curated selection of 20 profiles


And now ... drink and see the full array!
==========================================

Bon Appetit!