---
title: "Blood and Wine: The Wild Hunt"
output: 
  flexdashboard::flex_dashboard:
runtime: shiny
---
  
```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
library(readr)
library(tidyverse)
library(plotly)

# UTF fix

source.utf8 <- function(f) {
    l <- readLines(f, encoding="UTF-8")
    eval(parse(text=l),envir=.GlobalEnv)
}

# include helper

source("r/chloropleth.R")
source("r/app_page1.r")

# load data
wine_file <- read_csv("data/wine_master.utf8.csv")
wine_master <- wine_file[,c(24,26:33)]
wine_bottles <- read_csv("data/wine_betas.utf8.csv")
mapPolys <- geojsonio::geojson_read("data/countries.geo.json", what = "sp")
names(mapPolys) = c("id","country")
#mergedMap = sp::merge(mapPolys,wine_master)

```

```{r}
### This chunk creates lists of names for the selectInput options 
head(wine_master)
wine_types <- sort(unique(wine_master$variety))
country_names <- sort(unique(wine_master$country))

#province_names <- sort(unique(wine_master$province))
#province_names <- sort(unique(wine_master$province)) %in% (input$countryNames)
vineyard_names <- sort(unique(wine_master$designation)) 
winery_names <- sort(unique(wine_master$winery))
```





Sidebar {.sidebar} 
=====================================

This is the side bar where we put our shit. to select what's gonna be displayed in the chlorpleth

```{r}
# shiny inputs defined here
selectInput(inputId = "wineType", label = "Wine Types", choices = wine_types, selected = NULL, multiple = TRUE, selectize = TRUE, width = NULL, size = NULL)

selectInput(inputId = "countryName", label = "Countries", choices = country_names, selected = NULL, multiple = TRUE, selectize = TRUE, width = NULL, size = NULL)

#selectInput(inputId = "provinceNames", label = "Province", choices = province_names, selected = NULL, multiple = TRUE, selectize = TRUE, width = NULL, size = NULL)

selectInput(inputId = "wineryName", label = "Wineries", choices = winery_names, selected = NULL, multiple = FALSE, selectize = TRUE, width = NULL, size = NULL)

selectInput(inputId = "feature4", label = "Feature 4", choices = c("a", "b", "c"), selected = NULL, multiple = FALSE, selectize = TRUE, width = NULL, size = NULL)

selectInput(inputId = "feature5", label = "Feature 5", choices = c("a", "b", "c"), selected = NULL, multiple = FALSE, selectize = TRUE, width = NULL, size = NULL)

sliderInput(inputId = "priceRange", label = "Price Range", min = 0, max = 10000, value= c(10,100), step = NULL, round = FALSE,
  format = NULL, locale = NULL, ticks = TRUE, animate = FALSE,
  width = NULL, sep = ",", pre = NULL, post = NULL, timeFormat = NULL,
  timezone = NULL, dragRange = TRUE)
```

Identify your favourite flavours >> {data-orientation=rows}
===============================================================
Row {data-height=25}
--------------------------
Didn't you know there are many many ways to look at wine? Explore some ways below.

Row {data-height=500 .tabset .tabset-fade}
--------------------------

### Pricing

```{r}
page_1_price_dist(wine_master)

```

### Variety

```{r}
#page_1_variety_dist(wine_master)

variety_points_Graph <- ggplot(subset(wine_master, 
                                      variety %in% c("Pinot Noir","Chardonnay","Cabernet Sauvignon","Sauvignon Blanc","Syrah")
                              ),
              aes(points,fill=variety))+  
              geom_bar(na.rm=TRUE,
                      position="dodge")+
              theme(legend.position="bottom")+
              scale_x_discrete(name="Review Points") +
              scale_y_continuous(name="Number of Reviews")+
              ggtitle("Points by Top 5 Varieties")+
              theme(legend.position = "bottom")

variety_points_Graph <- ggplotly(variety_points_Graph)

variety_points_Graph
```

### Review Ratings

```{r}
#page_1_ratings_dist(wine_master)

review_Graph <- ggplot(wine_master,aes(points,fill=points))+geom_bar(na.rm=TRUE,fill="blue")+
  ggtitle("Distribution of Reviews by Points")+
  scale_x_continuous(name="Points in Review") +
  scale_y_continuous(name="Number of Reviews")+
  theme(legend.position = "none")+
  xlim(80,100)

review_Graph <- ggplotly(review_Graph)

review_Graph
```

### Country
```{r}
#page_1_country_dist(wine_master)

country_points_Graph <- ggplot(subset(wine_master, 
              country %in% c("France","Italy","Spain","Chile","United States of America")
                      ),
              aes(points,fill=country))+  
              geom_bar(na.rm=TRUE,
                      position="dodge")+
              theme(legend.position="bottom")+
              scale_x_continuous(name="Review Points") +
              scale_y_continuous(name="Number of Reviews")+
              xlim(80,100)+
              ggtitle("Reviews by Top 5 Countries")+
              theme(legend.position = "bottom")

country_points_Graph <- ggplotly(country_points_Graph)

country_points_Graph

```

Sample the relationships >> {data-orientation=rows}
===================================================

Row {data-height = 150}
------------------------

See how the different brands are related to each other

Row {.tabset, data-height = 500}
--------------------------------
### Prices for different countries

```{r}

country_price_Graph <- ggplot(subset(wine_master, 
              country %in% c("France","Italy","Spain","Chile","United States of America")
                      ),
              aes(price,fill=country))+  
              geom_bar(na.rm=TRUE,
                      position="dodge")+
              theme(legend.position="bottom")+
              scale_x_continuous(name="Review Points") +
              scale_y_continuous(name="Number of Reviews")+
              ggtitle("Prices by Top 5 Countries")+
              theme(legend.position = "bottom")

country_price_Graph <- ggplotly(country_price_Graph)

country_price_Graph

```

### Ratings for different prices

```{r}

price_points_Graph <- ggplot(wine_master,aes(points,price,group=points,color=points))+
  geom_boxplot(na.rm=TRUE)+
  scale_x_continuous(name="Review Points")+
  scale_y_continuous(name="Price of Wine ($)")+
  xlim(80,100)+
  ggtitle("Boxplot of Wine Price by Review Points")+
  theme(legend.position="none")

price_points_Graph <- ggplotly(price_points_Graph)

price_points_Graph
```

### Ratings for different varieties

```{r}
variety_points_Graph <- ggplot(subset(wine_master, 
                                      variety %in% c("Pinot Noir","Chardonnay","Cabernet Sauvignon","Sauvignon Blanc","Syrah")
                              ),
              aes(points,fill=variety))+  
              geom_bar(na.rm=TRUE,
                      position="dodge")+
              theme(legend.position="bottom")+
              scale_x_discrete(name="Review Points") +
              scale_y_continuous(name="Number of Reviews")+
              ggtitle("Points by Top 5 Varieties")+
              theme(legend.position = "bottom")

variety_points_Graph <- ggplotly(variety_points_Graph)

variety_points_Graph
```

Locate your favourite flavours >>
=================================
Inputs {.sidebar}
---------------------------------------------------------------------

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Price
```{r}
wines_by_price = wine_master[, c("country","price")]
mapByPrice = aggregate(wines_by_price, list( wines_by_price$country), median, na.action = na.omit)
pal <- colorBin("Blues", domain = mapByPrice$price, bins = 5, na.color = "white")
  
leaflet(sp::merge(mapPolys,mapByPrice)) %>% addPolygons(
    fillColor = ~pal(price),
    weight = 2,
    opacity = 1,
    color = "black",
    fillOpacity = 1.0
  ) %>% addLegend(pal = pal, values = ~price, opacity = 0.7, title = NULL,
                  position = "bottomright")
```
### Topics

And now ... Drink and view the entire array!{data-orientation=columns}
======================================================================
Inputs {.sidebar}
---------------------------------------------------------------------------------
```{r}

numericInput(inputId = "labels", label = "Number of Labels", min = 50, max = nrow(wine_master), value= 500)

```

Column
--------------------------------------------------------------------------------
```{r}
renderTable({
  wine_sample <- sample(nrow(wine_master), as.integer(input$labels))
  wine_master[wine_sample,]
})

```